---
title: "`reticulate`"
author: "Jay Lee"
date: "April 4, 2018"
output: ioslides_presentation
---

## Setup

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
library(ggplot2)
library(nycflights) # all flights out of EWR, JFK, LGA in 2017
data(flights)
```

## Access R objects from Python chunks

```{python}
import pandas
flights = r.flights # call R objects from python chunk with `r.object`
flights = flights[(flights['dest'] == "PDX") & (flights['dep_delay'] < 500)]
flights = flights[['carrier', 'dep_delay', 'arr_delay']]
flights = flights.dropna()
```


## Access Python objects from R chunks

```{r message = FALSE, warning = FALSE}
# automatically converts an R DF into a Pandas DF, and vice versa
# call Python objects from R with `py$object`
ggplot(py$flights, aes(dep_delay, arr_delay, col = carrier)) + geom_point() + geom_abline()
```

## Source a Python script

```{r warning = FALSE, message = FALSE}
cat(readLines("add.py"), sep="\n")
source_python('add.py')
add(15, -4)
```

## Use Python functions and modules "natively" in R

```{r}
np <- import('numpy', convert = FALSE) # turn off default conversion to R
a <- np$array(c(1:4))
sum <- a$cumsum()
rsum <- py_to_r(sum) # explicitly convert to R object

sum # a python (numpy) array
rsum # an R vector
```

## Some notes

* Indexing, 1 v. 0

* Permissions when installing python packages

* Not fully interactive in RStudio yet (daily builds)

* Kinda finicky

* Other things: access main Python module (environment) from R, iterators, use built-in functions (like `print`) with `import_builtins()`

* `repl_python()`

## Thank you :))))))

Code for slides at https://github.com/jayleetx/mLab/tree/master/reticulate_slides

https://rstudio.github.io/reticulate/index.html